%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PB - One Page Two Column Resume
% LaTeX Template
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{pb-resume}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\rfoot{Page \thepage \hspace{1pt}}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Patrick}{Bennett}{ \urlstyle{same}
\href{mailto:patrickisgreat@gmail.com}{patrickisgreat@gmail.com} | 404.514.7647
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{The Internet}
M.I.T. OpenCourseWare \\
MDN Web Docs \\
LaraCasts \\
Udemy \\
Stack OverFlow \\
GitHub \\

\sectionsep

\subsection{Wallace State College}
\descript{Computer Science}
\location{2000 - 2002 | Hartselle, AL}
\sectionsep

\subsection{North Cobb High School}
\location{Grad. 1999 |  Acworth, GA}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Facebook:// \href{https://facebook/paddy.bee.980}{\bf paddy.bee.980} \\
Github:// \href{https://github.com/patrickisgreat}{\bf patrickisgreat} \\
LinkedIn://  \href{https://www.linkedin.com/in/patrick-bennett-7769016}{\bf patrick-bennett-7769016} \\
Twitter://  \href{https://twitter.com/patrickisgreat}{\bf @patrickisgreat} \\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
JavaScript \textbullet{}  Python \textbullet{}  PHP \textbullet{}  \\
React \textbullet{}  Laravel \textbullet{}  Vue.js \textbullet{} 
Node.js \textbullet{}  Express.js \\ 
CSS \textbullet{} Sass \textbullet{} Less \textbullet{} HTML \\
GraphQL \textbullet{} REST \textbullet{}  SOAP\textbullet{} \\
MySQL\textbullet{}  Postgres\textbullet{}  SQL\textbullet{} \\
\sectionsep

\subsection{DevOps}
Linux CLI \textbullet{}  BASH \textbullet{}  Vim\textbullet{}  \\
Apache \textbullet{} Git (cli) \textbullet{} Docker \\
AWS \textbullet{} Kubernetes \textbullet{} CI / CD \textbullet{} \\
Jest \textbullet{} Mocha \textbullet{}  
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}
\runsubsection{Airbus}
\descript{| Sr. Software Engineer }
\location{September 2021 to present}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Full Stack: React / Next.js / Node / GraphQL / MongoDB.
\item Working on refactoring MVP application: SkyWise Predictive Maintenance, an application to help airlines keep track of the health of their fleet, and make predictions about future maintenance events.
\item Leading a small sub team on the effort to implement e2e, integration, and unit testing across the application. 
\item Built a mocking system for the graphql layer using mock service workers, cached static responses, and a simple routing system.
\item Traveling to France to interface with engineering teams and assist with PI planning for 10 week iterations.
\item Still fairly new at Airbus and continuing to absorb knowledge. 
\end{tightemize}
\sectionsep

\runsubsection{CNN / WarnerMedia }
\descript{| Sr. Software Engineer }
\location{March 2020 – September 2021}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Full stack React, JavaScript, and Python development on an agile team.
\item Improved performance and scalability of the LiveStory React / GraphQL application which gets millions of hits per day.
\item Improved performance and scalability of the cnn-data-api GraphQL service using k6, and Apollo Studio to identify and refactor bottlenecks in queries and api stitching.
\item Built failover REST api for LiveStory application.
\item Helped build first iteration of CNN+, CNN's forthcoming video streaming platform, within CNN's proprietary publishing platform.
\item Built DOM reconciliation features within CNN's Clay CMS to achieve reactive client side UI updates.
\item Built ClientModel implementation within Clay to allow for redux-esque client side state management across components.
\end{tightemize}
\sectionsep


\runsubsection{Digital Additive}
\descript{| Sr. Software Engineer }
\location{April 2015 - March 2020}
\begin{tightemize}
\item Shipped Vacoda - content management and creation system for corporate teams built in Laravel and Vue.js. This app is currently in production use by Home Depot CRM teams and Carters.com.
\item Configured Vacoda to ship to AWS EC2 instances via custom Docker containers with BitBucket Pipelines.
\item Built a product rating system for Home Depot.
\item Built various middleware and integrations for clients such as WeWork, IBM / Interact, and SouthernLinc to extend the functionality of Salesforce Marketing cloud.
\end{tightemize}  
\sectionsep

\runsubsection{BlacQube}
\descript{| Web Developer }
\location{May 2013 - April 2015 | Atlanta, GA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Built award winning mobile and web front ends for Mercedes and Mercedes-AMG.
\item Worked closely with designers to translate static designs into animated interactive experiences built with JavaScript and jQuery.
\item Upgraded cakePHP on the Mercedes-AMG Private Lounge web app. 
\item Administered web servers hosting various builds.
\end{tightemize}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
