%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% PB - One Page Two Column Resume
% LaTeX Template
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 

% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[]{pb-resume-openfonts}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
 
\rfoot{Page \thepage \hspace{1pt}}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Patrick}{Bennett}{ \urlstyle{same}
\href{mailto:patrickisgreat@gmail.com}{patrickisgreat@gmail.com} | 404.514.7647
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{The Internet}
Coursera \\
M.I.T. OpenCourseWare \\
MDN Web Docs \\
LaraCasts \\
Udemy \\
Stack OverFlow \\
GitHub \\

\sectionsep

\subsection{Wallace State College}
\descript{Computer Science}
\location{2000 - 2002 | Hartselle, AL}
\sectionsep

\subsection{North Cobb High School}
\location{Grad. 1999 |  Acworth, GA}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/patrickisgreat}{\bf patrickisgreat} \\
LinkedIn://  \href{https://www.linkedin.com/in/patrick-bennett-7769016}{\bf patrick-bennett-7769016} \\
StackOverflow:// \href{https://stackoverflow.com/users/864159/funkenstein}{\bf funkenstein} \\
Portfolio:// \href{https://patrickisgreat.com/}{patrickisgreat.com} \\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
JavaScript \textbullet{}  Python \textbullet{}  PHP \textbullet{} C++ \\
React \textbullet{}  Laravel \textbullet{}  Vue.js {} \\
Node.js \textbullet{}  Express \textbullet{} NestJS \\ 
CSS \textbullet{} Sass \textbullet{} Less \textbullet{} HTML \\
GraphQL \textbullet{} REST \textbullet{}  SOAP \\
MySQL \textbullet{}  Postgres
\sectionsep

\subsection{DevOps}
Linux CLI \textbullet{}  BASH \textbullet{}  Vim \\
Git (cli) \textbullet{} Docker \\
AWS \textbullet{} Lambda \textbullet{} CloudFormation  \\
Kinesis \textbullet{} DynamoDB  \\
Jest \textbullet{} Pytest \textbullet{} Mocha 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}
\runsubsection{Airbus}
\descript{| Sr. Software Engineer }
\location{September 2021 to present}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}

\item Proposed and implemented the Atlanta Experience Center: customized a realistic A320 model in Microsoft Flight Simulator, constructed a 3D cockpit, and integrated with SkyWise for demo purposes to high-level stakeholders.
\item Team Lead: Architected the NOO (Network Operations Optimization) data pipelines, a solution suite for real-time airline logistics, leveraging Python, Serverless, FastAPI, AWS Lambda, DynamoDB, Kinesis, and SQS.
\item Developed the sasipy library, providing comprehensive interfaces and types for GE's SASI-Q API, enabling developer friendly data modeling and integration.
\item Led a subteam to instate comprehensive testing (e2e, integration, unit) across SkyWise Predictive Maintenance, and built a GraphQL mocking system.
\item Traveled internationally to collaborate with engineering teams and spearheaded PI planning for 10-week iterations.

\end{tightemize}
\sectionsep

\runsubsection{CNN / WarnerMedia }
\descript{| Sr. Software Engineer }
\location{March 2020 – September 2021}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Improved performance and scalability of the LiveStory React / GraphQL application, a high-traffic application used for live news feeds.
\item Improved performance of the cnn-data-api GraphQL service using k6, and Apollo Studio to identify and refactor bottlenecks in queries and api stitching.
\item Built failover REST api for LiveStory application to support higher traffic during the Presidential election.
\item Helped build very early iteration of CNN+, a video streaming platform, before going back to Livestory. 
\item Built DOM reconciliation features within CNN's Clay CMS to achieve reactive client side UI updates.
\item Built ClientModel implementation within Clay to allow for redux-esque client side state management across components.
\end{tightemize}
\sectionsep


\runsubsection{Digital Additive}
\descript{| Sr. Software Engineer }
\location{April 2015 - March 2020}
\begin{tightemize}
\item Develpoed and Deployed Vacoda - content management and creation system for corporate teams built in Laravel and Vue.js. This app is currently in production use by Home Depot CRM teams and Carters.com.
\item Configured Vacoda to ship to AWS EC2 instances via custom Docker containers with BitBucket Pipelines.
\item Built a product rating system for Home Depot.
\item Built various middleware and integrations for clients such as WeWork, IBM / Interact, and SouthernLinc to extend the functionality of Salesforce Marketing cloud.
\end{tightemize}  
\sectionsep

\runsubsection{BlacQube}
\descript{| Web Developer }
\location{May 2013 - April 2015 | Atlanta, GA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Built award winning mobile and web front ends for Mercedes and Mercedes-AMG.
\item Worked closely with designers to translate static designs into animated interactive experiences built with JavaScript and jQuery.
\item Upgraded cakePHP on the Mercedes-AMG Private Lounge web app. 
\item Administered web servers hosting various builds.
\end{tightemize}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
